\documentclass[a4paper,10pt]{article}

\usepackage[T1]{fontenc}

\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks,pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{eurosym}
\usepackage{xcolor}
\usepackage{xfrac}
\usepackage{vwcol} 
\usepackage{adjustbox}
\definecolor{myBlue}{rgb}{0,0,0.55}


\hypersetup{
    urlcolor = {[rgb]{0,0,0}}
}

\newcommand\dunderline[3][-1pt]{{%
  \sbox0{#3}%
  \ooalign{\copy0\cr\rule[\dimexpr#1-#2\relax]{\wd0}{#2}}}}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\usepackage{geometry}
\geometry{top=0.3cm, bottom=0.5cm, left=0.4cm, right=0.4cm}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-1pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2\vspace{-0.8pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{1.15pt}
  \small
  \item
    \begin{tabular*}{0.97\textwidth}{l @{\extracolsep{\fill}}r}
      \normalsize{\textbf{#1}}   & #2 \\
      \small{#3} & #4 \\
    \end{tabular*}
  \vspace{1.5pt}
}

\def\Plus{\texttt{+}}

% -------- ORIGINAL ------------

\newcommand{\resumeSubItem}[2]{
    \small{\resumeItem{#1}{#2}\vspace{-4pt}}
	
}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}


\newcommand{\resumeProjectListStart}{\begin{minipage}{0.97\textwidth} 
                                     \begin{itemize}[leftmargin=5mm]
                                     \vspace{3pt}}
\newcommand{\resumeProjectListEnd}{\end{itemize} 
                                   \end{minipage}}
\newcommand{\resumeProjectItem}[1]{
    \item\small{#1}
    }

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


%----------HEADING-----------------
\begin{center}
  \begin{minipage}{0.97\textwidth}
      \begin{minipage}[c]{0.6\linewidth}
          \huge \textbf{Ulysse \textsc{Boucherie}}
          \\
          \emph{\large{DevOps Engineer \& Data Scientist (MSc.)}}
      \end{minipage}
      \hfill
      \begin{minipage}[c]{0.215\linewidth}
          \begin{tabular*}{\textwidth}{c@{\extracolsep{\fill}} l}
              \href{mailto:uboucherie1@gmail.com}{\raisebox{-0.055\height}{\faEnvelope}} & \href{mailto:uboucherie1@gmail.com}{\small{uboucherie1@gmail.com}} \\
              \href{https://github.com/odysseu}{\raisebox{-0.035\height}{\faGlobe}} & \href{https://odysseu.github.io/}{\small{odysseu.github.io}} \\
              \href{https://github.com/odysseu}{\raisebox{-0.035\height}{\faGithub}} & \href{https://github.com/odysseu}{\small{odysseu}} \\
              \href{https://www.linkedin.com/in/ulysse-boucherie-7a3b2b111/}{\raisebox{-0.0925\height}{\faLinkedinSquare}} & \href{https://www.linkedin.com/in/ulysse-boucherie-7a3b2b111/}{\small{in/ulysse.boucherie}} \\
              {\raisebox{-0.0925\height}{\faHome}} & \small{Fontainebleau, France}
          \end{tabular*}
      \end{minipage}
  \end{minipage}
  \end{center}


%------------PROJET-----------------------

\begin{center}
\begin{minipage}{0.95\textwidth}
    \centering
    \large \textbf{DevOps and data engineer upgrading public sector's processes}
\end{minipage}
\end{center}

\vspace{-5mm}

%-----------EXPERIENCE-----------------
\section{Experience}

\resumeSubHeadingListStart

\vspace{0.75mm}


\resumeSubheading{Ministry of the Interior}{Paris, France}{Data Scientist}{2024 - Present}

Responsible for publications on economic and financial crime
\resumeProjectListStart
\resumeProjectItem{Redesigned the team's ETL processes, reducing the delay between data acquisition and production by over 80\%.}
\resumeProjectItem{Implemented a culture of change with modern tools and methods for a diverse audience in terms of adaptability, technical skills, and ambition.}
\resumeProjectItem{Developed internal and open-source tools for the industrialized publication of articles and content for the general public.}
\resumeProjectItem{Co-designed, developed, and deployed LLM models to cluster free-text survey responses.}
\resumeProjectListEnd

\resumeSubheading{INSEE}{Nantes, France}{DevOps Engineer}{2021 -- 2024}

Development and support for INSEE's data science platform
\resumeProjectListStart
\resumeProjectItem{Co-developed and installed the Platform As A Service (\href{https://github.com/InseeFrLab/onyxia}{Onyxia}).}
\resumeProjectItem{Developed and implemented a new cutting-edge technical stack (Docker, Helm, GitLab and GitHub pipelines, Grafana, Prometheus, Vault) and accelerated production deployment by 10x.}
\resumeProjectItem{Provided support to data scientists, from beginners to advanced, for integrating their services (notebooks, internal data visualization applications, IDEs: RStudio \& PyCharm).}
\resumeProjectListEnd

\resumeSubheading{INSEE}{Nantes, France}{Data Platform Engineer}{2020 -- 2021}

System administrator for the internal data science platform
\resumeProjectListStart
\resumeProjectItem{Implemented components enabling 500+ INSEE data scientists to save up to 80\% of their time in deploying internal tools and studies.}
\resumeProjectItem{Set up monitoring and supervision of processes to manage shared physical resources (Windows Server). Optimized resource usage by 20\%.}
\resumeProjectItem{Initiated projects to translate code to move away from a proprietary data analysis license that had been in place for 20 years.}
\resumeProjectListEnd

\resumeSubheading{Central Statistics Office}{Dublin, Ireland}{End-of-studies Internship}{2020}
Statistical Assistant
\resumeProjectListStart
\resumeProjectItem{Co-edited the official report on Ireland's annual statistics.}
\resumeProjectItem{Developed specifications for the automatic reading of monthly meteorological records from over 250 years ago.}
\resumeProjectListEnd

% \resumeSubheading{Safran Aircraft Engines}{Villaroche, France}{Engineering Internship in Aero-Mechanical Optimization}{2018 (6 months)}
% \resumeProjectListStart
% \resumeProjectItem{Development of a new method for parameterizing engine blades based on a Bézier surfaces representation. Development and implementation of Python scripts for aero-mechanical optimization workflows.}
% \resumeProjectListEnd

\resumeSubHeadingListEnd


\vspace{-5mm}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\vspace{0.75mm}


\resumeSubheading{ENSAI}{Rennes, France}{Engineering Degree (MSc.)}{2018 -- 2021}
\resumeProjectListStart
\resumeProjectItem{\textit{Specialization in Computer Science}: Big Data.}
\resumeProjectItem{\textit{Core Curriculum}: Bayesian statistics, HPC, optimization.}
\resumeProjectListEnd

\resumeSubheading{Lycée François Premier}{Fontainebleau, France}{Preparatory Classes for Grandes Écoles}{2015 -- 2018}
\resumeProjectListStart
\resumeProjectItem{\textit{MPSI -- MP}: Mathematics - Physics - Engineering Sciences - Computer Science Specialization.}
\resumeProjectListEnd

\resumeSubHeadingListEnd


\vspace{-4mm}

%-----------TECHNICAL SKILLS + LANGUAGES -----------------
\begin{minipage}[t]{0.65\linewidth}
    \section{Technical Skills}
    \resumeSubHeadingListStart
    \resumeSubItem{Programming}{Python, Java, JavaScript, TypeScript, R, Bash, Go}
    \resumeSubItem{Infrastructure}{Docker, Kubernetes, Helm, CI/CD (GitLab, GitHub)}
    \resumeSubItem{Databases}{PostgreSQL, DuckDB}
    \resumeSubItem{Cloud Platforms}{Google Cloud Platform (GCP), Amazon Web Services (AWS)}
    \resumeSubHeadingListEnd
    \end{minipage}
\hfill
\begin{minipage}[t]{0.3\linewidth}
    \section{Languages}
    \resumeSubHeadingListStart
    \resumeSubItem{French}{Native}
    \resumeSubItem{English}{Bilingual}
    \resumeSubItem{Spanish}{Fluent}
    \resumeSubHeadingListEnd
\end{minipage}


% \vspace{0.5mm}

%-----------PROJECTS-----------------
\section{Personal Projects and Interests}
\vspace{0.5mm}
\begin{minipage}[t]{0.9865\textwidth}
\resumeSubHeadingListStart
  \resumeSubItem{Real Estate Web Application}{Optimization between renting and buying a property with real parameters \href{https://odysseu.github.io/HabitatCalc/}{HabitatCalc}.}
  \resumeSubItem{Tax Web Application}{Understanding marginal tax brackets on income and tax rates \href{https://odysseu.github.io/TrancheMaster/}{TrancheMaster}.}
  \resumeSubItem{Conferences and Seminars}{State Cloud 2026, INSEE and Public Statistical Services Webinars 2024 to 2026, AI Salon 2023, KubeCon 2023, DevFest 2022 \& 2023, VivaTech 2022}
  \resumeSubItem{Sports}{Triathlon, volleyball, alpine skiing, bouldering}
  \resumeSubItem{Music}{Piano (4 years), drums (10 years)}
\resumeSubHeadingListEnd
\end{minipage}


%-------------------------------------------
\end{document}